Re-fit

### 2023-01-17 scripts/r/04_refit/refit_jvc.Rmd
fix path

@@

>>>>

Currently, the GitHub repo "many_speech" is not available. We have added a zipped version of the GH repo archive (downloaded from OSF) to the OSF component.

@@

unzip(here("data", "analyses", "jvc", "cromileptes_saxatilis", "many_speech.zip"), exdir = here("data", "analyses", "jvc", "cromileptes_saxatilis"))
